---
title: "Report for the paper ..."
output: word_document
---

# Statistical Analysis

Continuous data are presented as mean±standard deviation while categorical variables as counts and percentages. Differences between groups were analyzed by the unpaired Student's t tests for continuous variables while.... To investigate the association between weight with sex, age and BMI, a linear regression was performed... A p-value <0.05 was considered statistically significant.

```{r, echo=TRUE}
library(lattice)
library(knitr)

set.seed(2015+5)
patient <- c(1:200)
height <- rnorm(200, 1.70, 0.1)
weight <- height + rnorm(200, 60, 10)
age <- rnorm(200, 60, 10)
sex <- sample(1:2, 200, replace = T)
sex <- factor(sex, levels = 1:2, labels = c("male", "female"))

dat <- data.frame(patient, height, weight, sex, age)
dat$BMI <- dat$weight/(dat$height^2)

fm1 <- lm(weight ~ sex + BMI + age, data = dat)
 
tab <- summary(fm1)$coefficients
```

```{r, echo=FALSE} 
kable(tab, dig = 4)
```

## Predict weight for 2 male patients with min and max BMI at different ages
```{r, echo=TRUE}
newdata <- with(dat, data.frame(
  sex = rep(1, each = 40),
  age = rep(seq(min(dat$age), max(dat$age), length = 20), each = 2),
  BMI = rep(c(min(dat$BMI), max(dat$BMI)), 20)
))

X <- model.matrix(~ sex + BMI + age, data = newdata)

betas <- summary(fm1)$coefficients[, 1]
newdata$pred <- c(X %*% betas)

newdata$BMI <- factor(newdata$BMI, labels = c("min BMI","max BMI"))
```

```{r, echo=FALSE, include=TRUE}
plot(dat$weight, dat$BMI, xlab = "weight", ylab = "BMI")
```

```{r, echo=FALSE}
xyplot(pred ~ age | BMI, type = "l", lty = c(1, 2, 2), cex = 1.8,  col = 1, lwd = 2, main = "age vs weight per BMI group", xlab = "age", ylab = "weight", data = newdata)
```


